\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

%---------- Margins ----------
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

%---------- Header ----------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%---------- Sections ----------
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

% Disable paragraph indentation so role lines aren't indented
\setlength{\parindent}{0pt}

% Give bullets a small indent so they nest under role titles nicely
\setlist[itemize]{noitemsep,nolistsep,leftmargin=1.5em}

%---------- Document ----------
\begin{document}

\begin{center}
    {\LARGE \textbf{Nadav Avital}} \\[4pt]
    \href{mailto:nadav.avital@icloud.com}{nadav.avital@icloud.com} \ $|$ \
    (650) 285-7786 \ $|$ \
    \href{https://linkedin.com/in/nadavital}{linkedin.com/in/nadavital} \ $|$ \
    \href{https://nadavavital.com}{nadavavital.com}
\end{center}

%---------- EXPERIENCE ----------
\section*{Professional Experience}

\textbf{eBay, San Jose}

\textit{Software Engineer – Global Technology, Buyer Experience} \hfill \textit{Feb 2025 -- Present}
\begin{itemize}
    \item Designed and implemented a backend \textbf{Java proxy server} for internal tools, with APIs that have been adopted by multiple checkout apps in production, providing services for secret management, SSO integration, role-based authentication, and Elasticsearch data access and index management.
    \item Built \textbf{FeedbackLens}, a generative AI–powered sentiment analysis dashboard in React, showing PMs and engineers a top down view of thousands of customer feedback entries, top concern summaries, and insights.
    \item Supported development on the \textbf{eBay iOS app}, collaborating with mobile engineers to deliver a seamless buyer experience, add new features, fix long in production bugs, and adapting to new OS releases.
    \item Contributed and added new features to \textbf{checkout and shopping cart experience services}, powering high-scale purchasing workflows across eBay and connecting our frontend and backend teams.
    \item Selected for eBay’s \textbf{AI Innovation Team}, helping drive adoption of AI-assisted software engineering practices across the company.
\end{itemize}

\textit{Software Engineering Intern – Core Technology, Payments} \hfill \textit{Jun -- Sep 2024}
\begin{itemize}
    \item Designed and implemented a \textbf{sentiment-analysis pipeline} in Python using APIs for generative AI integration, PII anonymization, and elastic search indexing.
    \item Created a Grafana dashboard displaying top insights and trends from the sentiment analysis pipeline that streamlined the checkout team’s ability to respond to customer feedback.
\end{itemize}

\textbf{Anodot, Ra’anana}

\textit{Software Engineering Intern} \hfill \textit{Jun -- Sep 2023}
\begin{itemize}
    \item Built a full-stack application to process Google Cloud usage data and generate optimization recommendations, enabling customer success managers to cut cloud costs for enterprise clients.
    \item Technologies: Python, JavaScript, SQL (MySQL/Redshift/BigQuery), Google Cloud APIs.
\end{itemize}

%---------- EDUCATION ----------
\section*{Education}
\textbf{University of California, Santa Barbara} \hfill \textit{Dec 2024} \\
B.S. Computer Science, GPA: \textbf{3.98}, Highest Honors, Dean's list 2021-2024

%---------- PROJECTS ----------
\section*{Projects}

\textbf{PlayCount} \hfill \textit{2024 -- Present}
\begin{itemize}
    \item Published iOS app that provides \textbf{Apple Music listening analytics}, including top songs, albums, and artists ranked by either play count or time listened.
    \item Enables users to explore detailed breakdowns such as top songs and albums by artist, and top songs within a specific album.
    \item Built in Swift/SwiftUI with MusicKit, MediaPlayer, and CloudKit, optimized for iOS 26 and styled to emulate the native Apple Music app.
    \item Integrated \textbf{App Intents} and \textbf{Shortcuts}, allowing Siri and system-level access (e.g., instantly retrieving the play count of the currently playing track).
\end{itemize}

\textbf{Split} \hfill \textit{Sep -- Dec 2024}
\begin{itemize}
    \item Cross-platform React Native app for splitting bills; integrated Venmo payments, image recognition, and receipt parsing APIs.
    \item Added in-app social layer with user profiles and friend requests, driving engagement beyond utility.
\end{itemize}

\textbf{Sous Chef} \hfill \textit{Mar -- Jun 2024}
\begin{itemize}
    \item VR cooking simulator in Unity/C\# with AI-driven guidance, teaching users real-world steak-cooking skills through immersive gameplay.
\end{itemize}

%---------- SKILLS ----------
\section*{Skills}
\textbf{Programming:} Swift, SwiftUI, Python, Java, JavaScript, C++, C\#, HTML/CSS, SQL, NoSQL \\
\textbf{Frameworks \& Tools:} MusicKit, CloudKit, React, Unity, Grafana, OpenAI APIs, GitHub, Figma \\
\textbf{Languages:} Fluent in English and Hebrew

\end{document}
